BOUT

### 2023-06-23 Data & Scripts/BOUT.Rmd
Auto stash before merge of "main" and "origin/main"

```{r BOUT MODEL 1}
BOUT.MOD1<-lmer(LDURATION~BEHAVIOR+SENTINEL_PRESENCE+GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+GROUP_SIZE+DISTURBANCE_FREQUENCY+(1|ID), data = BOUT)

@@

```{r BOUT MODEL 2}
BOUT.MOD2<-lmer(LDURATION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+BEHAVIOR*GROUP_SIZE+BEHAVIOR*BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|ID)+(1|VIDEO_ID), data = BOUT)

@@

In the second model with the added interactions, the behavior, generalized environment, group size and a number of interactions are significant.

The group size becoming significant is puzzling. I don't understand why now it would become significant.

@@

```{r BOUT MOD 3}
BOUT.MOD3<-lmer(LDURATION~BEHAVIOR+SENTINEL_PRESENCE+GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+GROUP_SIZE+BEHAVIOR*GENERALIZED_ENVIRONMENT*SENTINEL_PRESENCE+BEHAVIOR*GROUP_SIZE*SENTINEL_PRESENCE+BEHAVIOR*BAIT_PRESENCE+(1|ID), data = BOUT)

@@

Nice! The second model has the lowest AIC value and is therefore prefered.

@@

```{r RLMM MOD 2}
BOUT.RMOD2<-rlmer(LDURATION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+BEHAVIOR*GROUP_SIZE+BEHAVIOR*BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|ID), data = BOUT)

sjPlot::tab_model(BOUT.RMOD2
                  , show.re.var = T
                  , title = "Bout Robust Model 2 Output"
                  , dv.labels = " Effects of on duration of bouts of behaviors")
```

@@

-   Behavior, generalized environment and group size have significant effects. The former is to be expected, while the latter two are interesting, but not very informative (alone).
-   The interaction between behavior and generalized environment are significant. The effect size appears negative for both "head up" and "moving" behavior in green areas.
-   There is a significant interaction of sentinel presence and generalized environment.
-   There is a significant interaction of behavior and group size for head up and moving.
-   There is a significant interaction of "moving" and bait presence.

@@

#### Behavior X Generalized Environment

@@

Very interesting! Duration of bouts of alertness and moving remain largely the same, while the duration of foraging bout in green areas increases dramatically. \

@@

#### Sentinel Presence X Generalized Environment

@@

@@

#### Behavior x Bait Presence

>>>>

```{r BOUT MODEL 1}
BOUT.MOD1<-lmer(LDURATION~BEHAVIOR+SENTINEL_PRESENCE+GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+GROUP_SIZE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = BOUT)

@@

```{r BOUT MODEL 2}
BOUT.MOD2<-lmer(LDURATION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+BEHAVIOR*GROUP_SIZE+BEHAVIOR*BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = BOUT)

@@

In the second model with the added interactions, the behavior, generalized environment and a number of interactions are significant. The interaction between behavior and generalized environment is significant, as well as the interaction between the presence of a sentinel and generalized environment. The interaction between behavior and group size is significant. Lastly, moving and bait presence were significant.

@@

```{r BOUT MOD 3}
BOUT.MOD3<-lmer(LDURATION~BEHAVIOR*SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+GROUP_SIZE+(1|VIDEO_ID/ID), data = BOUT)

@@

Nice! The second model has the lowest AIC value and is therefore preferred.

@@

```{r RLMM MOD 2}
BOUT.RMOD2<-rlmer(LDURATION~BEHAVIOR*SENTINEL_PRESENCE+BEHAVIOR*GENERALIZED_ENVIRONMENT+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+BEHAVIOR*GROUP_SIZE+BEHAVIOR*BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = BOUT)

sjPlot::tab_model(BOUT.RMOD2
                  , show.re.var = T
                  , title = "Bout Robust Model 2 Output"
                  , dv.labels = " Effects on duration of bouts of behaviors")
```

@@

-   Behavior, generalized environment and group size have significant effects. The former is to be expected, while the latter two are interesting, but not very informative (alone).
-   The interaction between behavior and generalized environment are significant. The effect size appears negative for both "head up" and "moving" behavior in green areas.
-   There is a significant interaction of sentinel presence and generalized environment.
-   There is a significant interaction of behavior and group size
-   There is a significant interaction of "moving" and bait presence.

@@

### Behavior X Generalized Environment

@@

Very interesting! Duration of bouts of alertness and moving remain largely the same, while the duration of foraging bout in green areas increases dramatically.\

@@

### Sentinel Presence X Generalized Environment

@@

It could be that sentinels have a stabilizing effect on the duration of bouts

@@

### Behavior x Bait Presence
